{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2020-08-12 documents/microwave_spectrum.tex
Writing the protocol

\nwfilename{microwave_spectrum.pnw}\nwbegincode{1}\moddef{microwave_spectrum.py}\endmoddef\nwstartdeflinemarkup\nwenddeflinemarkup
import device_comms
import sweep
\nwendcode{}\nwbegindocs{2}\nwdocspar

\nwenddocs{}\nwbegincode{3}\moddef{}\endmoddef\nwstartdeflinemarkup\nwenddeflinemarkup

@@

>>>>

\nwfilename{microwave_spectrum.pnw}\nwbegincode{1}\moddef{microwave_spectrum.py}\endmoddef\nwstartdeflinemarkup\nwenddeflinemarkup
import sys
sys.path.append('/home/arthurdent/covidinator/firmware/eppendoofus/host/')

import device_comms
import sweep

\nwendcode{}\nwbegindocs{2}\nwdocspar

It cannot be overstated how sensitive this measurement is. At 12 GHz, merely bringing one's hand near the coaxial line almost doubled
the power sensor reading.

\nwenddocs{}\nwbegincode{3}\moddef{}\endmoddef\nwstartdeflinemarkup\nwenddeflinemarkup
import random

@@

We randomize \cite{first2000}

\nwenddocs{}\nwbegincode{5}\moddef{}\plusendmoddef\nwstartdeflinemarkup\nwenddeflinemarkup

\nwendcode{}\nwbegindocs{6}\nwdocspar
